Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated Changes
Work in progress.

    Biologically inspired algorithms have proven to be very effective when
    solving complex optimization problems
    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but
    the more challenging the problem, the more computing power it will require
    to solve them \cite{ontiveros2018high}. % You can add a comment on why it  
    % requires more power, the main reason is the fitness evaluation function - M 
    One technique to manage this
    processing power is to use distributed computing % To manage the processing power need or demand? - M
    \cite{thain2005distributed} or the cloud resources 
    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
    allows adaptating the required computing power according to the problem's
    complexity.

    Traditionally, bio-inspired algorithms are developed with a sequential
    (synchronous) perspective
    \cite{porto2018evolutionary,back1996evolutionary}, where a process must
    pause for the previous task to finish before continuing.
    % Add here a few current works that use the cloud and other distributed technologies - M
    In this research,
    we present a distributed algorithm built as a native cloud solution %, totally % fully, but this is hard to maintain - M
    % distributed
    , where its processes are executed asynchronously and in
    parallel. We designed the algorithm using the cloud available resources to
    distribute the processing workload among several computers or as a service
    in the cloud. 
    % The paragraph above is to repetitive, consider removing -  M
    This strategy allows to elastically increase (or reduce) the
    computing power according to the nature of the challenge
    \cite{armbrust2010view}.

    In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
    life-cycle of animal species. As in nature, population individuals grow older
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.
    % Just to be sure explain a bit more what we mean by extinsion. - M
    When this condition presents itself, it is required to create a new population
    to continue evolution (restart). 
    % Maybe you do it later, but explain what is a restart precisely 
    We previously used to generate a new random % In a previous work (reference) - M
    set of solutions, with the cost of losing all evolution knowledge.

>>>>

    Biologically inspired algorithms have proven to be very effective when
    solving complex optimization problems
    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but
    the more challenging the problem, the more computing power it will require
    to solve them \cite{ontiveros2018high}. We consider the main reason it requires 
    more computing power is related to the evaluation of the fitness function, 
    which means calculating the solution to the real problem our algorithm is searching for. 
    One technique to manage this
    processing power demand is to use distributed computing
    \cite{thain2005distributed} or the cloud resources 
    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy allows adaptation 
    of the required computing need according to the problem's complexity.

    Traditionally, bio-inspired algorithms are developed with a sequential
    (synchronous) perspective
    \cite{porto2018evolutionary,back1996evolutionary}, where a process must
    pause for the previous task to finish before continuing. 
    Some architectures address this issue \cite{valdez2021container,garcia2015evospace,merelo2016nodio} 
    by working on the cloud and finding solutions on distributed technologies.
    In this research, we present a distributed algorithm totally built as a 
    native cloud solution, where its processes execute asynchronously and in 
    parallel, managing the processing workload among several computers.  
    This strategy allows to elastically increase (or reduce) the
    computing power according to the nature of the challenge
    \cite{armbrust2010view}.

    In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
    life-cycle of animal species. As in nature, population individuals grow older % \cite{Felix-Saul2022}
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.
    % Just to be sure explain a bit more what we mean by extinsion. - M
    When this condition presents itself, it is required to create a new population
    to continue evolution (restart). 
    % Maybe you do it later, but explain what is a restart precisely 
    We previously used to generate a new random % In a previous work (reference) - M
    set of solutions, with the cost of losing all evolution knowledge.
